Seminar paper on Probabilistic Near-Duplicate Detection Using Simhash

### 2019-07-06 ii/paper/paper.tex
Stuff

The size of available features can vary significantly and is completely in the hand of the designer for a \emph{Simhash} implementation.
It's important to note, that there exists no clear guideline on which features of a data set are interesting and which features can be discarded.
The performance of a \emph{Simhash} implementation thereby also depends on the chosen features and the respective properties of the dataset.
Such features can be for instance binary chunks, file extension~\cite{inproc:simhash}, individual words, tags or URLs~\cite{inproc:main}.

After determining in which way feature are extracted from the original data, each feature is

@@

\cite{inproc:simhash}

>>>>

The size of available features can vary significantly and is completely in the hand of the designer for each \emph{Simhash} implementation.
It's important to note, that there exists no clear guideline on which features of a data set are interesting and which features can be ignored.
The performance of a \emph{Simhash} implementation thereby also depends on the chosen features and the respective properties of the dataset.
Such features can be for instance binary chunks, file extension~\cite{inproc:simhash}, individual words, tags or URLs~\cite{inproc:main}.

@@

After determining in which way feature are extracted from the original data, each feature is hashed and mapped onto a fingerprint, which represents the constellation of features.

The next challenge, which is the main topic this paper deals with, is to compare a fingerprint to all other fingerprints inside the given dataset.

\subsection{Weights and Hamming Distance}
